test_for_p.values

### 2017-12-08 test4pvalues.Rmd
working on the p value script

first the larger data

I am trying to display plots for each mouse. For each mouse I want to run the replicate line code.

>>>>

first the larger data 
seperate data into >20 cells or less

```{r}
twenty <- AP_mouse_table[AP_mouse_table$Ncells > 20,]
lessTwenty <- AP_mouse_table[AP_mouse_table$Ncells < 20,]
#these will give the list of mice

#subset MLH1_data by these lists

```
I am trying to display plots for each mouse. For each mouse I want to run the replicate line code.
